What public transit API logs tell us about travel flows

### 2016-01-15 paper.tex

Flow analysis involves the comparison of aggregated movement between distinct locations within a specific time frame. 
In most cases, the analytical objective is to identify trends that occur in journeys made between pairs of locations and allow for the sensitivities to be explored. 
Data visualization is typically employed to facilitate in this process thus the input data must be transformed into a format that allows for the quantity and directional flow of movement to be visually encoded.
The data must undergo several stages of data processing to arrive at this outcome.

@@

Next, the data is aggregated so that province level flow patterns are emphasized.
\cref{fig:method-ab} provides a diagrammatic representation of spatial aggregation on the basis of provincial administrative boundaries.
To compare the volume of flow between rural provincial areas and urbanized zones, train stations in major cities were aggregated into seperate groups. 
Simiarly, stations located outside of Belgium were aggregated to distinct group. 
A diagrammatic breakdown is depicted in \cref{fig:method-c} where color and shape is used to demarcate each group.
The following types of flows are observable from the outcome of aggregation:

>>>>

Flow analysis involves the comparison of aggregated movement between distinct locations within a specific time frame. 
In most cases, the analytical objective is to identify trends that occur in journeys made between pairs of locations and allow for their differences to be explored. 
Data visualization is typically employed to facilitate in this process thus the input data must be transformed into a format that allows for the quantity and directional flow of movement to be visually encoded.
The data must undergo several stages of data processing to arrive at this outcome.

@@

Next, the data is aggregated so that province level flow patterns are emphasized.
\cref{fig:method-ab} provides a diagrammatic representation of spatial aggregation on the basis of provincial administrative boundaries.
To compare the volume of flow between rural provincial areas and urbanized zones, train stations in major cities were aggregated into seperate groups. 
Similarly, stations located outside of Belgium were aggregated to distinct group. 
A diagrammatic breakdown is depicted in \cref{fig:method-c} where color and shape is used to demarcate each group.
The following types of flows are observable from the outcome of aggregation:
